\documentclass[11pt,a4paper]{article}
\usepackage{amsmath, amsthm, mathtools, fontenc, graphicx}
\usepackage{subcaption}
\input{latexmacros.tex}
\newcommand{\mycomment}[1]{}

\title{Model Checking BSML}
\author{N. Cohen, T. Coroneo, V. Iyer, G. Kaminer, and L. Madison}
\date{\today}
\hypersetup{pdfauthor={FP 2025, Group 3}, pdftitle={Model Checking BSML}}

\setlength{\parskip}{10pt plus 1pt minus 1pt}

\DeclareMathOperator{\botbot}{\rotatebox{90}{$\models$}}
\DeclareMathOperator{\toptop}{\raisebox{0pt}[0pt][0pt]{\rotatebox[origin=c]{270}{$\models$}}}

\begin{document}

\maketitle

\begin{abstract}
Bilateral State-based Modal Logic (BSML) was introduced in \cite{Aloni2022} to model Free-Choice (\textit{FC}) and related inferences which arise from speakers' distaste for
interpretations that verify a sentence by empty configuration (\textit{neglect-zero tendency}). To preclude such empty configurations, BSML uses state-based semantics (propositions evaluated at sets of worlds rather than individual worlds) and extends basic modal logic with a pragmatic enrichment function $[]^+$ which requires supporting states to be nonempty.
We implement an explicit model checker for $\mathrm{BSML}^{\gor}$, an extension of BSML with global disjunction, and use this to verify some properties, like Free-Choice inference, as described in \cite{Aloni2024}.
Further, we implement a type for representing Natural Deduction proofs for $\mathrm{BSML}^{\gor}$.
\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\clearpage

\input{Intro.tex}

\section{Model checking BSML}\label{sec:BSML}

This section describes the implementation of the explicit model checker for BSML.
More precisely, we will focus on $\mathrm{BSML}^{\gor}$, an extension of BSML with so-called \emph{global disjunction}.
This extension was not chosen for conceptual reasons, but merely to make the implementation of Natural Deduction more palatable, as we will see later.
Throughout this report, we will not need to differentiate between BSML and $\mathrm{BSML}^{\gor}$, so we will be somewhat sloppy and simply write BSML for our language.


\input{lib/Syntax.lhs}

\input{lib/Semantics.lhs}


\subsection{Verifying basic properties}

\begin{figure}[!h]
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \resizebox{\linewidth}{!}{%
            \begin{tikzpicture}[every node/.style={font=\LARGE}]
                \draw (2.5,13.75) circle (0.5cm) node {$w_p$};
                \draw (4.25,13.75) circle (0.5cm) node {$w_q$};
                \draw (2.5,11.5) circle (0.5cm) node {$w_{pq}$};
                \draw (4.25,11.5) circle (0.5cm) node {$w_{\emptyset}$};
                \draw [rounded corners=3.0] (1.75,14.75) rectangle (5.25,12.75);
                \draw [rounded corners=3.0] (3.5,14.5) rectangle (5,13);
                \draw [rounded corners=3.0] (1.5,15) rectangle (5.5,10.75);
            \end{tikzpicture}%
        }
        \caption{Example 3a}
        \label{fig:3a}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \resizebox{\linewidth}{!}{%
            \begin{tikzpicture}[every node/.style={font=\LARGE}]
                \draw (0.75,14.25) circle (0.5cm) node {$w_p$};
                \draw (3,14.25) circle (0.5cm) node {$w_q$};
                \draw (0.75,11.75) circle (0.5cm) node {$w_{pq}$};
                \draw (3,11.75) circle (0.5cm) node {$w_{\emptyset}$};
                \draw [rounded corners=3.0] (0,10.75) rectangle (3.75,12.5);
                \draw [rounded corners=3.0] (-0.25,15) rectangle (4,10.5);
                \draw [->, >=stealth] (1.25,11.75) .. controls (2.25,12) and (2,10.5) .. (1,11.25);
                \draw [->, >=stealth] (0.75,12.25) -- (0.75,13.75);
                \draw [->, >=stealth] (3,12.25) -- (3,13.75);
            \end{tikzpicture}%
        }
        \caption{Example 3b}
        \label{fig:3b}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \resizebox{\linewidth}{!}{%
            \begin{tikzpicture}[every node/.style={font=\LARGE}]
                \draw (0.75,14.25) circle (0.5cm) node {$w_p$};
                \draw (3,14.25) circle (0.5cm) node {$w_q$};
                \draw (0.75,11.75) circle (0.5cm) node {$w_{pq}$};
                \draw (3,11.75) circle (0.5cm) node {$w_{\emptyset}$};
                \draw [rounded corners=3.0] (0,11) rectangle (1.5,12.5);
                \draw [rounded corners=3.0] (-0.25,15) rectangle (3.75,10.75);
                \draw [->, >=stealth] (0.75,12.25) -- (0.75,13.75);
                \draw [->, >=stealth] (0.75,12.25) -- (3,13.75);
            \end{tikzpicture}%
        }
        \caption{Example 3c}
        \label{fig:3c}
    \end{subfigure}
    \caption{}
    \label{fig:all3}
\end{figure}

\input{test/semanticTests.lhs}

\section{Verifying inference}

\subsection{Pragmatic enrichment}
\input{lib/ML.lhs}

\subsection{Free-Choice inference}
The way FC-inference is now modelled, is that given a formula/statement like $\lozenge (\alpha \lor \beta)$ in $\mathrm{ML}$, we enrich it to obtain a formula $\mathrm{BSML}$:
\[
    [\lozenge (\alpha \lor \beta)]^+ = \lozenge ((\alpha \land \texttt{NE}) \lor (\beta \land \texttt{NE})) \land \texttt{NE}
\]
This formula more accurately represents the meaning of a sentence in linguistics, given speakers' distaste for null verification.
To accurately model FC, we should then be able to infer $\lozenge \alpha \land \lozenge \beta$ from $[\lozenge (\alpha \lor \beta)]^+$.

\input{test/simpletests.lhs}

\input{lib/lexer.lhs}


\input{lib/Parser.ly}

\input{exec/Main.lhs}

\input{lib/ND.lhs}

\input{test/ND_examples.lhs}

\section{Future work}
In the future, we would like to add an easier-to-navigate UI, which would help people interested in BSML 
but not well-versed in Haskell use our model-checker and be able to use our implementation of proofs as an interactive theorem prover. 
Increasing the efficiency of the model checker, possibly by representing models implicitly rather than explicitly, as in \cite{gattinger2024:software:SMCDEL} would of course also be an improvement.
This would allow larger classes of models and formulas to be checked in a reasonable amount of time.

Among the more fascinating (and ambitious) directions for future work would be extending the natural deduction representation we have described, to perform automated proof-search. 
Given that the natural deduction axiomatization is sound and complete, this would be a very powerful tool with which to explore these logics.

Until then, we hope you have enjoyed using our model-checker as much as we loved making it! Special thanks 
to Maria for her wonderful paper, and to Malvin for providing an environment where we could explore and learn 
something rather wonderful and exciting - it was a joy to work on the project, and we hope that it is a meaningful contribution to a fascinating field of study. 

\addcontentsline{toc}{section}{Bibliography}
\bibliographystyle{alpha}
\bibliography{references.bib}

\end{document}
